\textit{Associations between chlorophyll \emph{a} and various microcystin-LR health advisory concentrations}

### 2016-01-22 manuscript/f1000_submission/manuscript.tex
closer to submission ready for f1000

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Original default rstudio/pandoc latex file
%% upated by @jhollist 09/15/2014
%% inspired by @cboetting https://github.com/cboettig/template and
%% @rmflight blog posts:
%% http://rmflight.github.io/posts/2014/07/analyses_as_packages.html 
%% http://rmflight.github.io/posts/2014/07/vignetteAnalysis.html).  
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt,]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use microtype if available
\IfFileExists{microtype.sty}{\usepackage{microtype}}{}
\usepackage{graphicx}
% Redefine \includegraphics so that, unless explicit options are
% given, the image width will not exceed the width of the page.
% Images get their normal width if they fit onto the page, but
% are scaled down if they would overflow the margins.
\makeatletter
\def\ScaleIfNeeded{%
  \ifdim\Gin@nat@width>\linewidth
    \linewidth
  \else
    \Gin@nat@width
  \fi
}
\makeatother
\let\Oldincludegraphics\includegraphics
{%
 \catcode`\@=11\relax%
 \gdef\includegraphics{\@ifnextchar[{\Oldincludegraphics}{\Oldincludegraphics[width=\ScaleIfNeeded]}}%
}%
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Associations between chlorophyll a and various microcystin-LR health advisory Concentrations},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\setcounter{secnumdepth}{5}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Changes borrowed from @cboettig, added by @jhollist 
% A modified page layout 
\textwidth 6.75in
\oddsidemargin -0.15in
\evensidemargin -0.15in
\textheight 9in
\topmargin -0.5in
\usepackage{lineno} % add 
  \linenumbers % turns line numbering on 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%Packages and layout changes by @jhollist 09/15/2014
\usepackage{ragged2e}
\usepackage[font=normalsize]{caption}
  \usepackage[doublespacing]{setspace}
\usepackage{parskip}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\rfoot{\today}
\lfoot{\thepage}
%%Changed default abstract width and added lines
\renewenvironment{abstract}{
  \hfill\begin{minipage}{1\textwidth}
  \rule{\textwidth}{1pt}\vspace{5pt}
  \normalsize
  \begin{justify}
  \bfseries\abstractname\vspace{5pt}
  \end{justify}}
  {\par\noindent\rule{\textwidth}{1pt}\end{minipage}
}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Associations between chlorophyll \emph{a} and various microcystin-LR
health advisory Concentrations}
\author{
Jeffrey W. Hollister
Betty J. Kreakie
}
\date{}

\begin{document}
%%Edited by @jhollist 09/15/2014
%%Adds title from YAML
\begin{singlespace}
\begin{center}
\huge Associations between chlorophyll \emph{a} and various microcystin-LR
health advisory Concentrations
\end{center}
%%Adds Author, correspond email asterisk, and affilnum from YAML
\begin{center}
\large
Jeffrey W. Hollister \textsuperscript{*} \textsuperscript{1} 
Betty J. Kreakie \textsuperscript{1} 
\end{center}
%%Adds affiliations from YAML
\begin{justify}
\footnotesize \emph{ 
\\*
\textsuperscript{1}US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA\\*
}
%%Adds corresponding author email(s) from YAML
\newcounter{num}
\setcounter{num}{1}
\\[0.1cm]
\footnotesize \emph{ 
\ifnum\value{num}=1%
\textsuperscript{*} corresponding author:
\fi
\href{mailto:hollister.jeff@epa.gov}{\nolinkurl{hollister.jeff@epa.gov}}
\stepcounter{num}
}
\end{justify}
%%Adds date from YAML
\normalsize

\end{singlespace}

\singlespace

\vspace{2mm}

\hrule

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use. However, compared to other water
quality measures, field measurements of microcystin are not commonly
available due to cost and advanced understanding required to interpret
results. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and \emph{in situ}, and used
as a first defense against high levels of microcystin. Chlorophyll
\emph{a} is commonly measured, can be estimated \emph{in situ}, and has
been shown to be positively associated with microcystin. In this paper,
we use this association to provide estimates of chlorophyll \emph{a}
concentrations that are indicative of a higher probability of exceeding
select health advisory concentrations for microcystin-LR. Using the 2007
National Lakes Assessment and a conditional probability approach, we
identify chlorophyll \emph{a} concentrations that are more likely than
not to be associated with an exceedance of a microcystin health advisory
level. We look at the recent US EPA health advisories for drinking water
as well as the World Health Organization levels for drinking water and
recreational use and identify a range of chlorophyll \emph{a}
thresholds. A 50\% chance of exceeding one of the specific advisory
microcystin concentrations of 0.3, 1, 1.6, and 2 \(\mu\)g/L is
associatied with chlorophyll \emph{a} concentration thresholds of 21.92,
77.2, 84.96, and 105.84, respectively. When managing for these various
microcystin levels, exceeding these reported chlorophyll \emph{a}
concentrations should be a trigger for further testing and possible
management action.

\vspace{3mm}

\hrule

\doublespace

@@

In the 2007 NLA, microcystin-LR concentrations ranged from 0.05 to 225
\(\mu\)g/L. Microcystin-LR concentrations of 0.05 \(\mu\)g/L represent
the detection limits. Any value greater than that indicates the presence
of microcystin-LR. Of those lakes with microcystin, the median
concentration was 0.51\(\mu\)g/L and the mean was 3.17\(\mu\)g/L. Of all
lakes sampled, 21\% of lakes exceeded the USEPA Child level, 8.8\% of
lakes exceeded the USEPA Adult level, 11.7\% of lakes exceeded the WHO
Drinking level, and 7.3\% of lakes exceeded the WHO Recreational level.
For chlorophyll \emph{a}, the range was 0.07 to 936 \(\mu\)g/L. All
lakes had reported chlorophyll \emph{a} concentrations that exceeded
detection limits. The median concentration was 7.79 \(\mu\)g/L and the
mean was 29.63 \(\mu\)g/L. The associations between chlorophyll \emph{a}
and the upper confidence interval across a range of conditional
probability values are shown in Table \ref{tab:mc_chla_table}. Specific
chlorophyll \emph{a} that are associated with greater than even odds of
exceeding the advisory levels were 0.07, 0.07, 2.78, and 9.97\(\mu\)g/L
for 0.3, 1.0, 1.6, and 2.0 \(\mu\)g/L advisory levels, respectively
(Table \ref{tab:mc_chla_table} \& Figure \ref{fig:multi_cp_plot}).

The chlorophyll \emph{a} cutoffs may be used to predict whether or not a
lake exceeds the microcystin-LR health advisories. Doing so allows us to
compare the accuracy of the prediction as well as evaluate false
negatives. Total accuracy of the four cutoffs predicting microcystin-LR
exceedances were 19\% for the USEPA children's advisory, 22\% for the
WHO drinking water advisory, 22\% for the USEPA adult advisory, and 23\%
for the WHO regreational advisory (Tables \ref{tab:child_conmat_table},
\ref{tab:who_drink_conmat_table}, \ref{tab:adult_conmat_table}, \&
\ref{tab:who_rec_conmat_table}). However, total accuracy is only one
part of the prediction performace with which we are concerned.

@@

This is the case as the probability of exceeding each of the four tested
health advisory levels increases as a function of chlorophyll \emph{a}
concentration (Figure \ref{fig:multi_cp_plot}). We used this association
to identify chlorophyll \emph{a} concentrations that are associated with
a range of probabilities of exceeding a given health advisory level
(Table \ref{tab:mc_chla_table}). For the purposes of this discussion we
focus on a conditional probability of 50\% or greater (i.e., greater
than even odds to exceed a health advisory level). The 50\% conditional
probability chlorophyll \emph{a} thresholds represents 29.2\%, 9.8\%,
8.6\%, and 6.9\% of sample lakes for the USEPA Child, the WHO Drinking,
the USEPA Adult, and the WHO recreational levels, respecitvely.

@@

\newpage

\section{Figures}\label{figures}

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/chla_micro_scatter-1.pdf}
\caption{Scatterplot showing association betweeen chlorophyll \textit{a}
and microcystin-LR. \label{fig:chla_micro_scatter}}
\end{figure}

\newpage

\begin{figure}[htbp]
\centering
\includegraphics{manuscript_files/figure-latex/epa_child_cp_plot-1.pdf}
\caption{Conditional probability plots showing association between the
probability of exceeding various microcystin-LR (MLR) health advisory
Levels. A.) Plot for USEPA Child (0.3 \(\mu\)g/L). B.) Plot for WHO
Drinking (1 \(\mu\)g/L). C.) Plot for USEPA Adult (1.6 \(\mu\)g/L). D.)
Plot for WHO Recreational (2 \(\mu\)g/L). \label{fig:multi_cp_plot}}
\end{figure}

\newpage

@@

\begin{tabular}{l|l|l}
\hline
Source & Type & Concentration\\
\hline
USEPA & Adult Drinking Water Advisory & 1.6 \$\textbackslash{}mu\$g/L\\
\hline
USEPA & Child Drinking Water Advisory & 0.3 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Drinking Water & 1 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Recreational: High Prob. of Effect & 20-2000 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Recreational: Low Prob. of Effect & 2-4 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Recreational: Moderate Prob. of Effect & 10-20 \$\textbackslash{}mu\$g/L\\
\hline
WHO & Recreational: Very High Prob. of Effect & >2000 \$\textbackslash{}mu\$g/L\\
\hline
\end{tabular}

:Various suggested microcystin-LR health advisory concentrations.
\label{tab:microcystin_levels}

\newpage

\begin{tabular}{r|r|r|r|r}
\hline
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO Recreational\\
\hline
0.1 & 0.07 & 0.07 & 0.07 & 1.17\\
\hline
0.2 & 0.07 & 4.48 & 10.67 & 18.24\\
\hline
0.3 & 2.78 & 17.49 & 31.59 & 50.26\\
\hline
0.4 & 9.97 & 38.73 & 69.19 & 76.80\\
\hline
0.5 & 21.92 & 77.20 & 84.96 & 105.84\\
\hline
0.6 & 38.73 & 103.20 & 133.20 & 228.24\\
\hline
0.7 & 63.94 & 138.24 & 244.80 & 871.20\\
\hline
0.8 & 113.14 & 326.88 & 326.88 & 871.20\\
\hline
0.9 & 166.63 & 516.00 & 871.20 & 871.20\\
\hline
\end{tabular}

:Chlorophyll \textit{a} concentrations that are associated with a 50\%
probability of exceeding a microcystin-LR health advisory concentration.
\label{tab:mc_chla_table}

\newpage

\begin{tabular}{l|r|r|r}
\hline
  & Not Exceed & Exceed & Row Totals\\
\hline
Not Exceed & 638 & 93 & 731\\
\hline
Exceed & 173 & 124 & 297\\
\hline
Column Totals & 811 & 217 & 1028\\
\hline
\end{tabular}

:Confusion matrix comparing chlorophyll \textit{a} predicted exceedences
(rows) versus real exceedances (columns) for the USEPA childrens
drinking water advisory. \label{tab:child_conmat_table}

\newpage

\begin{tabular}{l|r|r|r}
\hline
  & Not Exceed & Exceed & Row Totals\\
\hline
Not Exceed & 850 & 82 & 932\\
\hline
Exceed & 57 & 39 & 96\\
\hline
Column Totals & 907 & 121 & 1028\\
\hline
\end{tabular}

:Confusion matrix comparing chlorophyll \textit{a} predicted exceedences
(rows) versus real exceedances (columns) for the WHO drinking water
advisory. \label{tab:who_drink_conmat_table}

\newpage

\begin{tabular}{l|r|r|r}
\hline
  & Not Exceed & Exceed & Row Totals\\
\hline
Not Exceed & 887 & 57 & 944\\
\hline
Exceed & 50 & 34 & 84\\
\hline
Column Totals & 937 & 91 & 1028\\
\hline
\end{tabular}

:Confusion matrix comparing chlorophyll \textit{a} predicted exceedences
(rows) versus real exceedances (columns) for the USEPA adult drinking
water advisory. \label{tab:adult_conmat_table}

\newpage

\begin{tabular}{l|r|r|r}
\hline
  & Not Exceed & Exceed & Row Totals\\
\hline
Not Exceed & 910 & 52 & 962\\
\hline
Exceed & 43 & 23 & 66\\
\hline
Column Totals & 953 & 75 & 1028\\
\hline
\end{tabular}

:Confusion matrix comparing chlorophyll \textit{a} predicted exceedences
(rows) versus real exceedances (columns) for the WHO recreational water
advisory. \label{tab:who_rec_conmat_table}

\newpage

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% For more detailed article preparation guidelines, please see:
% http://f1000research.com/author-guidelines

\documentclass[10pt,a4paper,twocolumn]{article}
\usepackage{f1000_styles}
\usepackage{hyperref}
\usepackage{longtable}
\bibliography{manuscript}

\begin{document}

%Still need to figure out how to get corresponding author on here.
\title{\textit{Associations between chlorophyll \emph{a} and various microcystin-LR
health advisory concentrations} }
\author[1]{Jeffrey W. Hollister}
\author[1]{Betty J. Kreakie}
\affil[1]{US Environmental Protection Agency, Office of Research and Development,
National Health and Environmental Effects Research Laboratory, Atlantic
Ecology Division, 27 Tarzwell Drive Narragansett, RI, 02882, USA}

\maketitle
\thispagestyle{fancy}

\begin{abstract}

Cyanobacteria harmful algal blooms (cHABs) are associated with a wide
range of adverse health effects that stem mostly from the presence of
cyanotoxins. To help protect against these impacts, several health
advisory levels have been set for some toxins. In particular, one of the
more common toxins, microcystin, has several advisory levels set for
drinking water and recreational use. However, compared to other water
quality measures, field measurements of microcystin are not commonly
available due to cost and advanced understanding required to interpret
results. Addressing these issues will take time and resources. Thus,
there is utility in finding indicators of microcystin that are already
widely available, can be estimated quickly and in situ, and used as a
first defense against high levels of microcystin. Chlorophyll \emph{a}
is commonly measured, can be estimated \emph{in situ}, and has been
shown to be positively associated with microcystin. In this paper, we
use this association to provide estimates of chlorophyll a
concentrations that are indicative of a higher probability of exceeding
select health advisory concentrations for microcystin-LR. Using the 2007
National Lakes Assessment and a conditional probability approach, we
identify chlorophyll \emph{a} concentrations that are more likely than
not to be associated with an exceedance of a microcystin health advisory
level. We look at the recent US EPA health advisories for drinking water
as well as the World Health Organization levels for drinking water and
recreational use and identify a range of chlorophyll \emph{a}
thresholds. A 50\% chance of exceeding one of the specific advisory
microcystin concentrations of 0.3, 1, 1.6, and 2 g/L is associatied with
chlorophyll \emph{a} concentration thresholds of 24.64, 65.6, 89.71, and
94.93, respectively. When managing for these various microcystin levels,
exceeding these reported chlorophyll \emph{a} concentrations should be a
trigger for further testing and possible management action.

\end{abstract}

\clearpage

@@

In the 2007 NLA, microcystin-LR concentrations ranged from 0.05 to 225
\(\mu\)g/L. Microcystin-LR concentrations of 0.05 \(\mu\)g/L represent
the detection limits. Any value greater than that indicates the presence
of microcystin-LR. Of those lakes with microcystin, the median
concentration was 0.51\(\mu\)g/L and the mean was 3.17\(\mu\)g/L. Of all
lakes sampled, 21\% of lakes exceeded the USEPA Child level, 8.8\% of
lakes exceeded the USEPA Adult level, 11.7\% of lakes exceeded the WHO
Drinking level, and 7.3\% of lakes exceeded the WHO Recreational level.
For chlorophyll \emph{a}, the range was 0.07 to 936 \(\mu\)g/L. All
lakes had reported chlorophyll \emph{a} concentrations that exceeded
detection limits. The median concentration was 7.79 \(\mu\)g/L and the
mean was 29.63 \(\mu\)g/L. The associations between chlorophyll \emph{a}
and the upper confidence interval across a range of conditional
probability values are shown in Table \ref{tab:mc_chla_table}. Specific
chlorophyll \emph{a} that are associated with greater than even odds of
exceeding the advisory levels were 0.07, 0.07, 2.98, and 10.67\(\mu\)g/L
for 0.3, 1.0, 1.6, and 2.0 \(\mu\)g/L advisory levels, respectively
(Table \ref{tab:mc_chla_table} \& Figure \ref{fig:multi_cp_plot}).

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{hollister_microcystin_fig2.jpg}
\caption{\label{fig:multi_cp_plot}Conditional probability plots showing association between the probability of exceeding various microcystin-LR (MLR) health advisory Levels. A.) Plot for USEPA Child (0.3 $\mu$g/L). B.) Plot for WHO Drinking (1 $\mu$g/L). C.) Plot for USEPA Adult (1.6 $\mu$g/L). D.) Plot for WHO Recreational (2 $\mu$g/L).  }
\end{figure}

The chlorophyll \emph{a} cutoffs may be used to predict whether or not a
lake exceeds the microcystin-LR health advisories. Doing so allows us to
compare the accuracy of the prediction as well as evaluate false
negatives. Total accuracy of the four cutoffs predicting microcystin-LR
exceedances were 19\% for the USEPA children's advisory, 21\% for the
WHO drinking water advisory, 22\% for the USEPA adult advisory, and 23\%
for the WHO regreational advisory (Tables \ref{tab:child_conmat_table},
\ref{tab:who_drink_conmat_table}, \ref{tab:adult_conmat_table}, \&
\ref{tab:who_rec_conmat_table}). However, total accuracy is only one
part of the prediction performace with which we are concerned.

@@

\begin{figure}
\centering
\includegraphics[width=0.4\textwidth]{hollister_microcystin_fig2.jpg}
\caption{\label{fig:chla_micro_scatter}Scatterplot showing association betweeen chlorophyll \textit{a} and microcystin-LR. }
\end{figure}

This is the case as the probability of exceeding each of the four tested
health advisory levels increases as a function of chlorophyll \emph{a}
concentration (Figure \ref{fig:multi_cp_plot}). We used this association
to identify chlorophyll \emph{a} concentrations that are associated with
a range of probabilities of exceeding a given health advisory level
(Table \ref{tab:mc_chla_table}). For the purposes of this discussion we
focus on a conditional probability of 50\% or greater (i.e., greater
than even odds to exceed a health advisory level). The 50\% conditional
probability chlorophyll \emph{a} thresholds represents 27.9\%, 11.3\%,
9\%, and 6.9\% of sample lakes for the USEPA Child, the WHO Drinking,
the USEPA Adult, and the WHO recreational levels, respecitvely.

@@

\onecolumn

@@

\begin{table}[ht]
\centering
\caption{Various suggested microcystin-LR health advisory 
                     concentrations.} 
\label{microcystin_levels}
\begin{tabular}{lll}
  \hline
Source & Type & Concentration \\ 
  \hline
USEPA & Adult Drinking Water Advisory & 1.6 \$mu\$g/L \\ 
  USEPA & Child Drinking Water Advisory & 0.3 \$mu\$g/L \\ 
  WHO & Drinking Water & 1 \$mu\$g/L \\ 
  WHO & Recreational: High Prob. of Effect & 20-2000 \$mu\$g/L \\ 
  WHO & Recreational: Low Prob. of Effect & 2-4 \$mu\$g/L \\ 
  WHO & Recreational: Moderate Prob. of Effect & 10-20 \$mu\$g/L \\ 
  WHO & Recreational: Very High Prob. of Effect & $>$2000 \$mu\$g/L \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Chlorophyll \textit{a} concentrations that are 
                     associated with a 50% probability of exceeding a 
                     microcystin-LR health advisory concentration.} 
\label{mc_chla_table}
\begin{tabular}{rrrrr}
  \hline
Cond. Probability & USEPA Child & WHO Drink & USEPA Adult & WHO Recreational \\ 
  \hline
0.10 & 0.07 & 0.07 & 0.07 & 1.22 \\ 
  0.20 & 0.07 & 4.43 & 11.80 & 20.00 \\ 
  0.30 & 2.98 & 20.43 & 31.40 & 53.64 \\ 
  0.40 & 10.67 & 42.24 & 66.96 & 82.22 \\ 
  0.50 & 23.36 & 66.96 & 83.52 & 105.84 \\ 
  0.60 & 38.30 & 103.20 & 133.20 & 155.52 \\ 
  0.70 & 65.60 & 166.63 & 871.20 & 216.00 \\ 
  0.80 & 117.50 & 338.40 & 871.20 & 871.20 \\ 
  0.90 & 167.04 & 516.00 & 871.20 & 871.20 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA childrens drinking water advisory.} 
\label{child_conmat_table}
\begin{tabular}{rrr}
  \hline
Not Exceed & Exceed & Row Totals \\ 
  \hline
649 &  96 & 745 \\ 
  162 & 121 & 283 \\ 
  811 & 217 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO drinking water advisory.} 
\label{who_drink_conmat_table}
\begin{tabular}{rrr}
  \hline
Not Exceed & Exceed & Row Totals \\ 
  \hline
839 &  77 & 916 \\ 
   68 &  44 & 112 \\ 
  907 & 121 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the USEPA adult drinking water advisory.} 
\label{adult_conmat_table}
\begin{tabular}{rrr}
  \hline
Not Exceed & Exceed & Row Totals \\ 
  \hline
883 &  57 & 940 \\ 
   54 &  34 &  88 \\ 
  937 &  91 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\begin{table}[ht]
\centering
\caption{Confusion matrix comparing chlorophyll \textit{a} 
                     predicted exceedences (rows) versus real exceedances 
                     (columns) for the WHO recreational water advisory.} 
\label{who_rec_conmat_table}
\begin{tabular}{rrr}
  \hline
Not Exceed & Exceed & Row Totals \\ 
  \hline
910 &  52 & 962 \\ 
   43 &  23 &  66 \\ 
  953 &  75 & 1028 \\ 
   \hline
\end{tabular}
\end{table}

\newpage
\twocolumn
